Eurovision Song Contest: semifinal 1, 2009

### 2020-07-29 inst/eurovision.Rmd
make eurovision hyper2 pnames be character, not factor
more detail

competitors <- jj[1:18]
colnames(preference) <- jj      # voters; 20 countries (18 + DE + UK)
rownames(preference) <- competitors

@@

Now, take the first row of `preference`.  This represents the votes
cast *by* (sic) Montenegro (`"ME"`).  Their favourite was [last
column] Bosnia & Herzegovina (`"BA"`), who they gave rank 1 to.  Their
second favourite was Macedonia, their third was Turkey, and so on.
They were not allowed to vote for themselves, which is why the first
column is `NA`.  So the order was: `BA` (1), `MK` (2) , `TR` (3), `IS`
(4), `RO` (5), `IL` (6), `AM` (7), `FI` (8), `BY` (9), `MT` (10).  The
other countries (`CZ`, `BE`, `SW`, `CH`, `BG`, `PT`) did not receive
any points from Montenegro.  We need to convert matrix `preference`
into a likelihood function, here `eurovision2009`:

>>>>

competitors <- as.character(jj[1:18])
colnames(preference) <- jj      # voters; 20 countries (18 + DE + UK)
rownames(preference) <- competitors

@@

Now, take the first row of `preference`.  This represents the votes
cast *by* (sic) Montenegro (`"ME"`).  Their favourite was [last
column] Bosnia & Herzegovina (`"BA"`), who they gave rank 1 to.  Their
second favourite was Macedonia, their third was Turkey, and so on.
They were not allowed to vote for themselves, which is why the first
column is `NA`.  So the order was: `BA` (1), `MK` (2) , `TR` (3), `IS`
(4), `RO` (5), `IL` (6), `AM` (7), `FI` (8), `BY` (9), `MT` (10).  The
other countries (`CZ`, `BE`, `SW`, `CH`, `BG`, `PT`) did not receive
any points from Montenegro.  The rows show the votes cast by each
country; note the final two rows corresponding to votes cast by
Germany and the UK, who did not compete and therefore cast votes for
all competitors.

We need to convert matrix `preference` into a likelihood function,
here `eurovision2009`:
